Active Learning from Blackbox to Timed Connectors

### 2016-04-18 shortpaper/paper.tex
.

When applying active automata learning on some model, we assume that the model should be equivalent
to some \emph{Mealy machine}, i.e., a deterministic model accepting a finite set of inputs and
mapping them to a finite set of outputs.

Such a model is encapsulated as a \emph{teacher} by the \emph{Oracle}, which handles
all communication with the model. The oracle also serves as a so-called \emph{Minimal Adequate
Teacher} \cite{DBLP:journals/iandc/Angluin87}
interface, which is responsible for two types of queries.

\begin{itemize}
  \item[-] \textbf{Membership Query} (hereinafter referred to as \emph{mq}) In grammar-learning
    \cite{DBLP:journals/iandc/Angluin87}, \emph{mq} checks if a word is a member of certain language
    defined by the given grammar. When it comes to
    automata learning, \emph{mq} is supposed to provide \emph{simulation results} for given input
    sequences.
  \item[-] \textbf{Equivalence Query} (hereinafter referred to as \emph{eq}) Given a hypothesis
    (usually constructed by the learning algorithm), \emph{eq} checks whether the hypothesis is
    equivalent to the system-under-learn and generates a counter-example if needed. Generally,
    \emph{eq} is irrealizable when SUL is a blackbox. So we tactically use $mq$ to achieve the
    approximate results.
\end{itemize}

@@

\subsection{Observation Table}
\emph{Observation Tables}, proposed in \cite{DBLP:journals/iandc/Angluin87}, are used to construct
hypothetical Mealy machines from the results of membership queries.

Mealy machines consist of \emph{states} and \emph{transitions}.
As for blackboxes, input sequence $s\in\mathcal{I}^*$ can be used to denote its state 
after executing $s$. Similarly, for all $a\in\mathcal{I}$, we use $sa$ to denote the successor
state of $s$ after executing $a$.
However, under such notations, there are \emph{infinite} number of states, among which most are
duplicate.

@@

%%\begin{figure}[ht]
  %%\begin{center}
    %%\begin{displaymath}
      %%\begin{array}{l||ccccc||c}
        %%\hline
        %%& (a,\rread) & (\bot,\rread) & (a,\rnoread) & (\bot,\rnoread) & T & acc\\
        %%\hline\hline
        %%\varepsilon & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon\\
        %%\hline
        %%(a,\rread) & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon\\
        %%(\bot,\rread) & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
        %%\rowcolor[gray]{.9}
        %%(a,\rnoread) & \rblock & \rblock & \rblock & \rempty & \rempty & unclosed\\
        %%(\bot,\rnoread) & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
        %%T & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
        %%\hline
      %%\end{array}
    %%\end{displaymath}
    %%% \input{./images/hypo.tex}
  %%\end{center}
  %%\caption{Observation Table and Corresponding Hypothesis}
  %%\label{fig:hypo}
%%\end{figure}

>>>>

When applying active automata learning on some model, we assume that the model should be equivalent
to some \emph{Mealy machine}.
Such a model is encapsulated as a \emph{teacher} by the \emph{Oracle}, which handles
all communication with the model. The oracle also serves as a so-called \emph{Minimal Adequate
Teacher} \cite{DBLP:journals/iandc/Angluin87}
interface, which is responsible for two types of queries.

\begin{itemize}
  \item[-] \textbf{Membership Query} (hereinafter referred to as \emph{mq}) In grammar-learning
    \cite{DBLP:journals/iandc/Angluin87}, \emph{mq} checks if a word is a member of certain language
    defined by the given grammar. When it comes to
    automata learning, \emph{mq} is supposed to provide \emph{simulation results} for given input
    sequences.
  \item[-] \textbf{Equivalence Query} (hereinafter referred to as \emph{eq}) Given a hypothesis
    (usually constructed by the learning algorithm), \emph{eq} checks whether the hypothesis is
    equivalent to the system-under-learn and generates a counter-example if needed. 
\end{itemize}

@@

\subsection{Observation Table}
\emph{Observation Tables}, proposed in \cite{DBLP:journals/iandc/Angluin87}, are used to describe
hypothetical Mealy machines in learning algorithm L*.

As mentioned before, Mealy machines consist of \emph{states} and \emph{transitions}. However in
blackboxes, we only have \emph{input sequences} and their corresponding \emph{outputs}.
Similarly, for all $a\in\mathcal{I}$, we use $sa$ to denote the successor
state of $s$ after executing $a$.
However, under such notations, there are \emph{infinite} number of states, among which most are
duplicate.

@@

\begin{figure}[ht]
  \begin{center}
    \footnotesize
    \begin{displaymath}
      \begin{array}{l||ccccc||c}
        \hline
        & (a,\rread) & (\bot,\rread) & (a,\rnoread) & (\bot,\rnoread) & T & acc\\
        \hline\hline
        \varepsilon & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon\\
        \hline
        (a,\rread) & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon\\
        (\bot,\rread) & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
        \rowcolor[gray]{.9}
        (a,\rnoread) & \rblock & \rblock & \rblock & \rempty & \rempty & unclosed\\
        (\bot,\rnoread) & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
        T & \rblock & \rblock & \rempty & \rempty & \rempty & \varepsilon \\
        \hline
      \end{array}
    \end{displaymath}
    % \input{./images/hypo.tex}
  \end{center}
  \caption{Observation Table and Corresponding Hypothesis}
  \label{fig:hypo}
\end{figure}
